\pkg{MRP-Kit} A `grammar' of multilevel regression with post-stratification and implementation in \proglang{R}

### 2020-10-04 paper/paper.tex

---
documentclass: jss
author:
  - name: Lauren Kennedy
    affiliation: Monash University
    email: \email{name@company.com}
    url: http://rstudio.com
  - name: Mitzi Morris
    affiliation: Columbia University
  - name: Jonah Gabry
    affiliation: Columbia University
  - name: Rohan Alexander
    affiliation: University of Toronto
title:
  formatted: "\\pkg{MRP-Kit} A 'grammar' of multilevel regression with post-stratification and implementation in \\proglang{R}"
  # If you use tex in the formatted title, also supply version without
  plain:     "A 'grammar' of multilevel regression with post-stratification and implementation in R"
  # For running headers, if needed
  short:     "\\pkg{foo}: A grammar of MRP"
abstract: >
  In this paper we define a grammar for multilevel regression with post-stratification (MRP) and implement this grammar in the R Package \pkg{MRPKit}. Our grammar is centered around the following verbs: add, remove, delete, and replace. These act on survey objects. Our grammar, and its implementation, provides a detailed workflow when conducting MRP that will be useful for researchers and in teaching.
keywords:
  # at least one keyword must be supplied
  formatted: [multilevel regression with post-stratification, "\\proglang{R}", reproducibility, statistics, political science]
  plain:     [multilevel regression with post-stratification, R, reproducibility, statistics, political science]
preamble: >
  \usepackage{amsmath}
output: rticles::jss_article
---

```{r, setup, include=FALSE}
options(prompt = 'R> ', continue = '+ ')
```

@@

We first define a grammar of MRP, which we define as the underlying rules and principles that are common to every analysis based on MRP. This grammar is based around the following verbs: 'add', 'remove', 'delete', and 'replace'. These verbs are applied to a survey object, a post-stratification object, and survey\_map object. These three objects come together to create a mapping object, which is what processes such as regression act on. Finally, common diagnostics and graphs are implemented. In this way, our grammar and package implement an entire statistical workflow for conducting MRP.

@@

Our grammar and package complements existing packages such as \proglang{survey} (ADD CITATION), X and Y. These packages... Instead, ours is focused on what is needed for MRP.

@@

MRP package - https://github.com/gelman/mrp

@@

The \proglang{MRPKit} package has the following key components: survey objects, which for most users will be a collection of two surveys where one is larger than the other; a survey map, that relates the survey objects and then an MRP object, which is created once the survey map is applied to the survey objects. Regression acts on the MRP object. These objects are subject to the following verbs: 'add', 'delete', 'new', and 'replace'. For instance: \proglang{SurveyMap\$add}, \proglang{SurveyOb\$delete}, \proglang{SurveyMap\$new}, and \proglang{SurveyMap\$replace}.

@@

% sampl <- surveyStr$new(...)
% pop <- surveyStr$new(...)
% map <- surveyMap$new(sampl, pop, ...)
% mrp1 <- MRP$new(sampl, pop, map)

% option 1
% mod1 <- mrp1$fit(y ~ x + (1|group))
% mod1 <- mrp1$fit(y ~ x + (1|group) + (1|group2))

% mod1$poststratify()
% mod2$poststratify("model1")

% or

% option 2
% mrp1$fit(y ~ x + (1|group), name = "model1")
% mrp1$fit(y ~ x + (1|group) + (1|group2), name = "model2")

% mrp1$poststartify("model1")
% mrp1$poststartify("model2")

@@

A `SurveyMap` object holds the mapping between a set of items in a survey and a population dataset. The label is the item label in each dataset and the values is a list of all possible values.   The values for the survey and population must be aligned, i.e., the lists must have the same number of elements and the values at index i in each list are equivalent.  If there is a meaningful ordering over the values, they should be listed in that order, either descending or ascending.

@@

>>>>

\documentclass[
]{jss}

\usepackage[utf8]{inputenc}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\author{
Lauren Kennedy\\Monash University \And Mitzi Morris\\Columbia University \And Jonah Gabry\\Columbia University \And Rohan Alexander\\University of Toronto
}
\title{\pkg{MRP-Kit} A `grammar' of multilevel regression with
post-stratification and implementation in \proglang{R}}

\Plainauthor{Lauren Kennedy, Mitzi Morris, Jonah Gabry, Rohan Alexander}
\Plaintitle{A `grammar' of multilevel regression with post-stratification and
implementation in R}
\Shorttitle{\pkg{foo}: A grammar of MRP}

\Abstract{
In this paper we define a grammar for multilevel regression with
post-stratification (MRP) and implement this grammar in the R Package
\pkg{MRPKit}. Our grammar is centered around the following verbs: add,
remove, delete, and replace. These act on survey objects. Our grammar,
and its implementation, provides a detailed workflow when conducting MRP
that will be useful for researchers and in teaching.
}

\Keywords{multilevel regression with post-stratification, \proglang{R}, reproducibility, statistics, political science}
\Plainkeywords{multilevel regression with post-stratification, R, reproducibility, statistics, political science}

%% publication information
%% \Volume{50}
%% \Issue{9}
%% \Month{June}
%% \Year{2012}
%% \Submitdate{}
%% \Acceptdate{2012-06-04}

\Address{
        }

% Pandoc header

\usepackage{amsmath}

\begin{document}

@@

We first define a grammar of MRP, which we define as the underlying
rules and principles that are common to every analysis based on MRP.
This grammar is based around the following verbs: `add', `remove',
`delete', and `replace'. These verbs are applied to a survey object, a
post-stratification object, and survey\_map object. These three objects
come together to create a mapping object, which is what processes such
as regression act on. Finally, common diagnostics and graphs are
implemented. In this way, our grammar and package implement an entire
statistical workflow for conducting MRP.

@@

Our grammar and package complements existing packages such as
\proglang{survey} (ADD CITATION), X and Y. These packages\ldots{}
Instead, ours is focused on what is needed for MRP.

@@

MRP package - \url{https://github.com/gelman/mrp}

@@

The \proglang{MRPKit} package has the following key components: survey
objects, which for most users will be a collection of two surveys where
one is larger than the other; a survey map, that relates the survey
objects and then an MRP object, which is created once the survey map is
applied to the survey objects. Regression acts on the MRP object. These
objects are subject to the following verbs: `add', `delete', `new', and
`replace'. For instance: \proglang{SurveyMap\$add},
\proglang{SurveyOb\$delete}, \proglang{SurveyMap\$new}, and
\proglang{SurveyMap\$replace}.

@@

\% sampl \textless- surveyStr\(new(...) % pop <- surveyStr
\)new(\ldots) \% map \textless-
surveyMap\(new(sampl, pop, ...) % mrp1 <- MRP
\)new(sampl, pop, map)

\% option 1 \% mod1 \textless-
mrp1\(fit(y ~ x + (1|group)) % mod1 <- mrp1
\)fit(y \textasciitilde{} x + (1\textbar group) + (1\textbar group2))

\% mod1\(poststratify() % mod2
\)poststratify(``model1'')

\% or

\% option 2 \% mrp1\(fit(y ~ x + (1|group), name = "model1") % mrp1
\)fit(y \textasciitilde{} x + (1\textbar group) + (1\textbar group2),
name = ``model2'')

\% mrp1\(poststartify("model1") % mrp1
\)poststartify(``model2'')

@@

A \texttt{SurveyMap} object holds the mapping between a set of items in
a survey and a population dataset. The label is the item label in each
dataset and the values is a list of all possible values. The values for
the survey and population must be aligned, i.e., the lists must have the
same number of elements and the values at index i in each list are
equivalent. If there is a meaningful ordering over the values, they
should be listed in that order, either descending or ascending.

@@

\end{document}
